Seminarium TI 3700\\ Data Analysis on Twitter: An Overview (working title)

### 2014-03-04 authorinstr_2.tex

\section{Tweet stream analysis}
\subsection{Statistics}
\subsection{User Modelling}
\subsection{User Classification}

\subsection{Tag based analysis}
\subsection{Event identification}

>>>>

\section{Tweet stream analysis}
\subsection{Statistics}
\subsection{User Modelling}
\subsection{User Classification}
User classification is the problem of classification of users based on (1) their metadata such as age, location and job and (2) the tweets a user has posted. In this chapter we will discuss some issues concerning User Classification and some use-cases.

\subsubsection{User Classification Issues}
\textbf{Context}\\
To classify users on their tweets is it useful to extract the context of the content of a tweet. Some hashtag $x$ could have a different context in two tweets. So extra information about the content of a tweet is needed. For instance \cite{userclasst} uses mentions of (members of) political parties to deduce if a certain hashtag is used in a political context. 
\\\\
\textbf{Profile}\\
Profile information can be helpful to classify a user, but it should be used with care due to the amount of fake, inconsistent or incorrect information. According to \cite{usermachine} 80\% of the users provide a location and 48\% of the users provide a short bio. Furthermore etnicity and gender are far more difficult to extract. 
\subsection{Tag based analysis}
\subsection{Event identification}
